Empirical Evaluation of eval in R

### 2020-08-18 inst/analysis/analysis_stable.Rmd
Facet wrap on eval_function for the classification

>>>>

### `expr` argument when it is a call

```{r expr_call_arg}
expr_call_arg <- eval_calls %>% filter(expr_expression_type == "LANGSXP") %>% 
  mutate(function_expr = map_chr(expr_expression, function_name))
```

The following top level functions are used:

```{r top_level_function_expr}
expr_call_arg %>% count(function_expr) %>% arrange(desc(n))
```

We can distinguish a few groups:

- assignments
- reading (in a data frame, a vector)
- parsing
- defusing (`quote` and so on)
- conversion or creation of new values
- building calls and calling
- working with environments
- class assignments, reads and definitions
- building logical values
- formula
- meta programming on functions (getting access to the body of the function, to the call stack)
- 'NA' corresponds to no function calls (or that it was not deparsed successfully)

```{r group_expr_functions}
group_expr_functions <- expr_call_arg %>% mutate(group_function_expr = fct_collapse(function_expr, 
                          assignment = c("<-", "[[<-", "[<-", "$<-"),
                          read = c("[", "[[", "$"),
                          parsing = c("parse", "str2lang", "str2expression", "parse_only", "base::parse"),
                          defusing = c("quote", "substitute", "bquote", "expr", "quo"),
                          expressions = c("as.list", "expression", "as.name", "as.expression", "list", "as.data.frame", "as.character", "{", "modify_lang"),
                          calling = c("call", "as.call", "do.call"),
                          environment = c("environment", "as.environment"),
                          classAssign = c("@<-"),
                          classRead = c("slot", "@"),
                          classDef = c(".Primitive(\"class\")"),
                          logical = c("<", ">", "is.element"),
                          choice = c("if"),
                          function_meta = c("sys.calls", "function", "body"),
                          formula = c("~", "deriv", "D", "model.frame", "rootftfunc", "contest.lmerModLmerTest", "JacFunc", "gamlss.family", "contest1D.lmerModLmerTest", "contestMD.lmerModLmerTest", "reexpr"),                           
                          other_level = "other" ))
                          #TODO: add anonymous function applications
```

```{r}
group_expr_functions %>% count(group_function_expr) %>% arrange(desc(n)) %>% knitr::kable()
```

```{r}
group_expr_functions %>% ggplot() +
  geom_bar(aes(x = fct_rev(fct_infreq(group_function_expr)))) +
  scale_y_sqrt() +
  coord_flip() +
  labs(title = "Category of calls", y = "n", x = "category" ) 
```

```{r }
group_expr_functions %>% ggplot() +
  geom_bar(aes(x = fct_rev(fct_infreq(group_function_expr)))) +
  scale_y_sqrt() +
  coord_flip() +
  labs(title = "Category of calls", y = "n", x = "category" ) +
  facet_wrap(vars(eval_function))
```
